---
title: Final Project-R"
author: "Jim Ryan"
date: "12-02-2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Final Project - #Brexit Tweet Analysis
In this problem, you will use R to do further analysis on the Twitter data collected in the python program.  Where relevant, you are encouraged to use functions from `dplyr` and `ggformula`.

Load necessary libraries here.
```{r, echo=FALSE}
library(tidyverse)
library(ggformula)
library(ggplot2)
library(data.table)
```

### Reading and cleaning the data
a. Read in file of tweet info created in python and summarizs

```{r}
Brexit_df <- fread("Brexit_tweets.csv",nrows=-1)
summary(Brexit_df)

Brexit_df$in_reply_to_screen_name[Brexit_df$in_reply_to_screen_name==""]<-NA # replace blank values with NA
 

nrow(unique(Brexit_df[,"tweet"])) # count unique tweets
nrow(unique(Brexit_df[,"screen_name"])) #Unique Screen Names



```
 

```{r}
 # turn True False vakues in tweet_is_Retweet with 1 for True and 0 for Flase and make it a factor
 
Brexit_df$tweet_is_Retweet=ifelse(Brexit_df$tweet_is_Retweet==TRUE,1,0)
 
 
Brexit_df$tweet_is_Retweet <- as.factor(Brexit_df$tweet_is_Retweet)

 
 

 
 
```
Create plots of sentiment as a factor of whether the tweet is a retweet
```{r}

ggplot(data=Brexit_df, aes(x=tweet_is_Retweet),color=green) +
    geom_bar(stat="count",fill='turquoise')+ggtitle("Count of Tweets and Retweets")+
  scale_x_discrete(labels = c('Tweet','Retweet')) 


 ggplot(Brexit_df) + 
  geom_boxplot(aes(factor(tweet_is_Retweet), polarity),color='red',show.legend = FALSE ) + 
  labs(title='Polarity Scores  of Tweets and Retweets for Brexit')+
  ylab("Polarity Score") +   
  xlab("Tweets and Retweets") +
  scale_x_discrete(labels = c('Tweets','Retweets'))

  ggplot(Brexit_df) + 
  geom_boxplot(aes(factor(tweet_is_Retweet), subjectivity),color='blue',show.legend = FALSE ) + 
  ylab("Subjectivity Score") +  
  xlab("Tweets and Retweets") +  
  labs(title='Subjectivity Scores of Tweets and Retweets for Brexit')+
  scale_x_discrete(labels = c('Tweets','Retweets'))
  
gf_dhistogram(~Brexit_df$polarity, bins = 20,color ='red',fill='blue',xlab = 'Polarity',title = 'Distribution of Tweet Polarity')

gf_dhistogram(~Brexit_df$subjectivity, bins = 10,color ='blue',fill='red',xlab = 'Subjectivity',title = 'Distribution of Tweet Subjectivity') 


                  
 

 

```


 T-test polarity 
```{r}
#subset dataframe into original tweets with polarity and subjectivbity columns
origtweet <- subset(Brexit_df, tweet_is_Retweet == 0, select = c("polarity","subjectivity","tweet_is_Retweet")) # subset original tweets  include polarity and subjectivity


#subset dataframe into retweets with polaarity and subjectivbity columns
retweet <- subset(Brexit_df, tweet_is_Retweet == 1, select = c("polarity","subjectivity","tweet_is_Retweet"))  # subset retweets  include polarity and subjectivity


t.test(origtweet$polarity, retweet$polarity, alternative = "two.sided") # T-test of polarity between tweets and retweets

 
 
t.test(origtweet$subjectivity, retweet$subjectivity, alternative = "two.sided") # T-test of subjectivity between tweets and retweets
```

# Polarity T-Test shows no statistically significant difference of polarity between tweets and retweets
# Subjectivity T-Test shows no statistically significant difference of subje between tweets and retweets
  .
